%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry {Senior Software Engineer \$Azure Devops Engineer} % Job title
  {SpyderTech} % Organization
  {Sydney} % Location
  {July. 2022 - Present} % Date(s)
  { }

  %---------------------------------------------------------
  \cventry {Senior Software Engineer} % Job title
  {Lake Maintenance} % Organization
  {Sydney} % Location
  {May. 2013 - July. 2022} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Everything that matters.} \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.} \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)} \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.} \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.} \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.} \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}\end{cvitems} }
  %---------------------------------------------------------
  \cventry {Director \& Software Engineer} % Job title
  {Andrew IT Services} % Organization
  {Sydney} % Location
  {Jan. 2017 - Present} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Designed on-boarding process to guide new engineers, help them to focus on the right tasks, and set expectations to help them be successful at Infrastructure team.} \item {Migrated the orchestration system from DC/OS to Kubernetes which is based on AWS EKS. Managed 3 Kubernetes clusters and 300+ pods. Managed all Kubernetes manifests declaratively with Kustomize and ArgoCD.} \item {Designed and managed complex network configurations on AWS with 4 VPC and 100+ subnets. Separated the development network and operation network according to financial regulations. Established dedicated network connections from AWS VPC to partners' on-premise network based on AWS Direct Connect with secure connection using IPsec VPN. Provisioned OpenVPN servers with LDAP integration.} \item {Provisioned a observability system with Kafka, Elastic Stack(Filebeat, Heartbeat, APM Server, Logstash, Elasticsearch, Kibana). Collected log, uptime, tracing data from hosts, containers, pods and more. The ES cluster which has 9 nodes processed more than 1 billion documents per month. Wrote Terraform module to easily provision ES cluster on AWS EC2 instances.} \item {Provisioned a monitoring system with Kafka, Telegraf, InfluxDB, Grafana. Collected metrics from hosts, containers, pods and more. Wrote Terraform module to easily provision InfluxDB with HA on AWS EC2 instances.} \item {Introduced Kong API Gateway to easily connect all API microservices with a declarative management method based on Terraform and Atlantis to collaborate and audit change history.} \item {Provisioned the Directory Service for employee identity management based on OpenLDAP which guarantees HA with multi-master replication.} \item {Implemented Worker microservices consuming Kafka event topics for email, SMS, Kakaotalk and Slack notification. Developed in-house framework to easily build Kafka consumer microservice with common features including retry on failure, DLQ(Dead Letter Queue), event routing and more.} \item {Introduced Elastic APM to help distributed tracing, trouble-shooting and performance testing in MSA.}\end{cvitems} }

  %---------------------------------------------------------
  \cventry {Software Engineer} % Job title
  {CSC} % Organization
  {Sydney} % Location
  {Nov. 2012 - Mar. 2013} % Date(s)
  { }

  %---------------------------------------------------------
  \cventry {Co-founder \& Software Engineer} % Job title
  {Electronic Mobile Pty Ltd} % Organization
  {Sydney} % Location
  {Jan. 2012 - Jan. 2016} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Designed on-boarding process to guide new engineers, help them to focus on the right tasks, and set expectations to help them be successful at Infrastructure team.} \item {Migrated the orchestration system from DC/OS to Kubernetes which is based on AWS EKS. Managed 3 Kubernetes clusters and 300+ pods. Managed all Kubernetes manifests declaratively with Kustomize and ArgoCD.} \item {Designed and managed complex network configurations on AWS with 4 VPC and 100+ subnets. Separated the development network and operation network according to financial regulations. Established dedicated network connections from AWS VPC to partners' on-premise network based on AWS Direct Connect with secure connection using IPsec VPN. Provisioned OpenVPN servers with LDAP integration.} \item {Provisioned a observability system with Kafka, Elastic Stack(Filebeat, Heartbeat, APM Server, Logstash, Elasticsearch, Kibana). Collected log, uptime, tracing data from hosts, containers, pods and more. The ES cluster which has 9 nodes processed more than 1 billion documents per month. Wrote Terraform module to easily provision ES cluster on AWS EC2 instances.} \item {Provisioned a monitoring system with Kafka, Telegraf, InfluxDB, Grafana. Collected metrics from hosts, containers, pods and more. Wrote Terraform module to easily provision InfluxDB with HA on AWS EC2 instances.} \item {Introduced Kong API Gateway to easily connect all API microservices with a declarative management method based on Terraform and Atlantis to collaborate and audit change history.} \item {Provisioned the Directory Service for employee identity management based on OpenLDAP which guarantees HA with multi-master replication.} \item {Implemented Worker microservices consuming Kafka event topics for email, SMS, Kakaotalk and Slack notification. Developed in-house framework to easily build Kafka consumer microservice with common features including retry on failure, DLQ(Dead Letter Queue), event routing and more.} \item {Introduced Elastic APM to help distributed tracing, trouble-shooting and performance testing in MSA.}\end{cvitems} }

  %---------------------------------------------------------
  \cventry {Software Engineer} % Job title
  {MIA International} % Organization
  {Sydney} % Location
  {May. 2010 - Dec. 2011} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Packer and Terraform.} \item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.} \item {Designed an overall service architecture and pipelines of the Machine Learning based Fashion Tagging API SaaS product with the micro-services architecture.} \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.} \item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.} \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}\end{cvitems} }

  %---------------------------------------------------------
  \cventry {Software Engineer} % Job title
  {Helecom System Pty Ltd} % Organization
  {Sydney} % Location
  {Jan. 2007 - Jun. 2010} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).} \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.} \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}\end{cvitems} }

  %---------------------------------------------------------
  \cventry {Software Engineer \& Security Researcher (Compulsory Military Service)} % Job title
  {Zhejiang Pan-China Software Co Ltd} % Organization
  {China} % Location
  {July. 2003 - July. 2004} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}\end{cvitems} }
  %---------------------------------------------------------
\end{cventries}